Reproducible Research Peer Assignment 1
========================================================
Loading and preprocessing the data


```{r,cache=TRUE}
fileUrl <-"https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = "activity.zip", method = "curl")
unzip("activity.zip")
activity <- read.csv("activity.csv")
```

Here is the mean total number of steps taken per day?

```{r,echo=FALSE}
totalSteps <- aggregate(steps ~ date, data = activity, sum)
meanStepsperDay <- mean(totalSteps$steps)
meanStepsperDay
```

Here is a histogram of the total number of steps taken each day
```{r fig.width=7, fig.height=6,echo=FALSE}
hist(activity$steps,main='Total steps per day',xlab='Steps per day', col='blue')
```
Mean and Median total number of steps taken per day


```{r,echo=FALSE}
mean(totalSteps$steps)
median(totalSteps$steps)
```

Here is the average daily activity pattern?
```{r fig.width=7, fig.height=6,echo=FALSE}
avgInterval <- aggregate (steps ~ interval, data = activity, mean, na.rm = TRUE)
plot(steps ~ interval, data = avgInterval, type = "l", main='Average Daily Activity')

```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
maxInterval <- avgInterval[which.max(avgInterval$steps), ]$interval
maxInterval

```
Imputing missing values:
Total missing values
```{r}
missing <- sum(is.na(activity))
missing
```
Filling the missing values
```{r}
newActivity = activity
newActivity[is.na(newActivity)] <- mean(totalSteps$steps)
summary(newActivity)
```

Create histogram and new mean and median
```{r fig.width=7, fig.height=6}
newSteps <- aggregate(steps ~ date, data = newActivity, sum)
hist(newSteps$steps,main='New steps per day',xlab='Steps per day', col='blue')
mean(newSteps$steps)
median(newSteps$steps)

```
Are there any difference in Activity patterns ? 
```{r}


```
